### 2015-05-22 results.tex
FPGA stuff and new caption command.
ping ipsec

@@

\begin{figure}[ht]
\input{graphs/openssh-bench}
\caption{file transfer over an SSH tunnel. The background stripped bars are the CPU usage.}
\label{fig:openssh-bench}
\end{figure}

@@

\begin{figure}[ht]
\input{graphs/openvpn-ftp-bench}
\caption{FTP file transfer over an OpenVPN tunnel. The background stripped bars are the CPU usage.}
\label{fig:openvpn-ftp-bench}
\end{figure}

@@

\begin{figure}[ht]
\input{graphs/ipsec-ftp-bench}
\caption{FTP file transfer over an IPSec tunnel. The background stripped bars are the CPU usage.}
\label{fig:ipsec-ftp-bench}
\end{figure}

@@

@@

\begin{figure}[ht]
\input{graphs/ftp-bench-comparison}
\caption{Comparison of file transfer methods. The background stripped bars are the CPU usage.}
\label{fig:ftp-bench-comparison}
\end{figure}

>>>>

\begin{figure}[ht]
\input{graphs/ipsec-ping-benchmark}
\caption{Ping min/avg/max response time}{for different packet sizes using IPsec. For each packet size, 1000 requests were flooded to the board, that is \textit{"outputs packets as fast as they come back or one hundred times per second, whichever is more"}, according to the \texttt{ping} command manual.}
\label{fig:ping-benchmark-ipsec}
\end{figure}

@@

\begin{figure}[ht]
\input{graphs/openssh-bench}
\caption{file transfer over an SSH tunnel. The background stripped bars are the CPU usage.}{}
\label{fig:openssh-bench}
\end{figure}

@@

\begin{figure}[ht]
\input{graphs/openvpn-ftp-bench}
\caption{FTP file transfer over an OpenVPN tunnel. The background stripped bars are the CPU usage.}{}
\label{fig:openvpn-ftp-bench}
\end{figure}

@@

\begin{figure}[ht]
\input{graphs/ipsec-ftp-bench}
\caption{FTP file transfer over an IPSec tunnel. The background stripped bars are the CPU usage.}{}
\label{fig:ipsec-ftp-bench}
\end{figure}

@@

The GCM performance presented clearly shows a drop of throughput and an increase of CPU usage, illustrating the fact that those operations are hard on the software.
With an hardware offload, we could expect not only a drastic drop of the CPU usage, but an increase of throughput as well, since it's CPU-limited in those results.
Note that they are achieved usinf a C-based implementation of galois-field multiplications.
As we saw in chapter~\ref{chap:theory}, modern processor designers tend to add specialized instruction set aimed at AES-GCM enhancement.
Should further tests be conducted concerning IPSec paired with GCM, it would be wise to compare with an assembly implementation exploiting ARM NEON instruction set.
Some are being developed~\cite{Conrado2013,Danilo2013}, but none have been committed to the Linux kernel repository yet.

@@

\begin{figure}[ht]
\input{graphs/ftp-bench-comparison}
\caption{Comparison of file transfer methods. The background stripped bars are the CPU usage.}{}
\label{fig:ftp-bench-comparison}
\end{figure}
